---
title: "Demand Shocks & Special Districts"
subtitle: "Evidence from Chinese Import Shocks"
format:
  niu-revealjs:
    self-contained: true
    embed-resources: true
author:
  - name: Christopher B. Goodman
    #orcid: 0000-0002-8565-9714
    email: cgoodman@niu.edu
    affiliations: Northern Illinois University
date: 2025-04-18
bibliography: references.bib
citations-hover: true
#suppress-bibliography: true
---

```{r setup}
#| message: FALSE
#| warning: FALSE
#| include: FALSE

library("tidyverse")
library("arrow")
library("haven")
library("readxl")
library("fixest")
library("modelsummary")
library("tinytable")
options(tinytable_html_mathjax = TRUE)


`%ni%` <- Negate(`%in%`)

datadir = "~/Library/CloudStorage/Dropbox/Data"
projectdir = "~/Library/CloudStorage/Dropbox/Projects/Papers"

# Run scripts
source(file.path(projectdir, "yellow-yard", "analysis", "scripts", "02_data-import-var-create.r"))

pre <- ipw_91_01 |>
  add_column(period = "1991-2001") |>
  left_join(ipw_o_91_01, by = "cz90")

post <- ipw_01_11 |>
  add_column(period = "2001-2011") |>
  left_join(ipw_o_01_11, by = "cz90")

analysis_vars <- bind_rows(pre, post) |>
  left_join(spdist_nt, by = c("cz90", "period")) |>
  select(-year) |>
  left_join(spdist_ne, by = c("cz90", "period")) |>
  select(-year) |>
  left_join(spdist_nx, by = c("cz90", "period")) |>
  select(-year) |>
  left_join(spdist_nt_start, by = c("cz90", "period")) |>
  select(-year) |>
  left_join(combined, by = c("cz90", "period")) |>
  select(-year)

falsification_vars <- bind_rows(pre, post) |>
  mutate(
    period = case_match(
      period,
      "1991-2001" ~ "1971-1981",
      "2001-2011" ~ "1981-1991"
    )
  ) |>
  rename(ipw_c = ipw) |>
  left_join(spdist_nt, by = c("cz90", "period")) |>
  select(-year) |>
  left_join(combined, by = c("cz90", "period")) |>
  select(-year)

```

##  {.center .large}

What is the importance of manufacturers in the creation and dissolution of special districts?

## Introduction

-   Special districts are a unique form of local government that provide a single service or a limited number of services
    -   A defining characteristic: *lack of durability*
    -   Special districts are created and dissolved frequently
-   What leads to these changes?
    -   Changes in demand for services
    -   Changes in state laws
    -   Changes in local politics

## Introduction

-   Manufacturers are often viewed as *boundary change entrepreneurs*
    -   Individuals (or groups of individuals) who seek to alter (or preserve) the boundaries of local governments for both collective and selective gain
    -   Identifying such individuals is exceedingly difficult outside of case studies
    -   Proxies or conditions conducive to the emergence of such entrepreneurs are used in the literature
-   If manufacturers (and their employees) become more or less important in the local area, what happens to special districts?
    -   Concern: Services provided by special districts may elevate manufacturers
    -   Solution: Look for shocks, instruments, or both

## Preview of results {visibility="hidden"}

-   Use Chinese import shocks, instrumented using @autor2013, to examine changes in the importance of manufacturers
    -   The rising threat of Chinese imports worked to diminish U.S. manufacturing, reaching and inflection in 2001 when China joins the World Trade Organization (WTO)
    -   Areas experienced this shock differently
-   A \$1,000 increase in import exposure per worker leads to between 1.9 and 3.1 district reduction among urban and urban adjacent commuting zones
    -   As manufacturers become less important in the local economy, the support for special district declines

## A primer on special districts {visibility="hidden"}
> *Special district governments are independent, special purpose governmental units that exist as separate entities with substantial administrative and fiscal independence from general purpose local governments* -- U.S. Census Bureau

-   *Administrative independence*
    -   A sufficiently independent governing board, elected or appointed (or both), without interference from other governments
-   *Fiscal independence*
    -   The ability to adopt a budget, levy taxes and/or fees, and issue debt without interference from other governments
-   Typically, a district is classified as "dependent" because of violations of administrative independence

## A primer on special districts {visibility="hidden"}

**Important features**

-   Typically single function

-   *Territorial flexibility*

    -   Can overlap other governments, including other special districts
    -   Borders are more easily changed
    -   Districts typically choose their constituents

-   Usually exempt from various laws governing general purpose governments

    -   Voting share may be apportioned on any number of bases, land ownership is most common

## A primer on special districts {visibility="hidden"}

::::: columns
::: {.column width="50%"}
-   Popular but growth has been slowing
-   Most common areas of specialization
    -   Fire protection
    -   Water supply
    -   Housing & community development
-   Net counts mask significant churn (many created and many dissolved each period)
:::

::: {.column width="50%"}
```{r importance-tbl}
#| message: FALSE
#| warning: FALSE
#| results: asis
#| echo: false

importance <- tribble(
  ~year, ~count, ~share,
  1972, 23885, 0.305364494,
  1982, 28078,	0.343335779,
  1992, 31555, 0.371431935,
  2002, 35052,	0.400479863,
  2012, 38266, 0.424913387,
  2022, 39555,	0.435450312
)

tt(importance, width = c(0.15, 0.30, 0.30)) |>
  setNames(c("Year", "No. of districts", "Share of all govts")) |>
  format_tt(j = 2, digits = 0, num_mark_big = ",") |>
  format_tt(j = 3, fn = scales::label_percent()) |>
  style_tt(j = 1:3, align = "lcc")

```
:::
:::::

## Why are special districts created? {visibility="hidden"}

-   To access public services or respond to changes in demand for public services [@burns1994; @foster1997]
-   In response to changes in state law, to circumvent restrictions on general purpose local governments [@goodmanleland2019]
-   Boundary change entrepreneurs seek to alter the system for their collective and selective benefit [@feiock2001]

## Why are special districts dissolved? {visibility="hidden"}

-   Creation in reverse?
    -   Some evidence for this with circumvention [@goodmanleland2025]
    -   Municipal TELs decrease dissolutions; municipal functional home rule increases dissolutions
-   The literature on dissolutions is small

## Boundary change entrepreneurs

-   Pivotal individuals (or groups of individuals) who,
    -   Get proposed boundary changes on the public agenda
    -   Shepherd such proposals through the political process
-   Creation (or preventing a dissolution) of a special district is the simplest form of boundary change [@carr2004]
-   Who are they?
    -   Public officials – Mayors and/or city councilors
    -   Businesses – Chambers of commerce, developers, **manufacturers**
    -   Residents – Civics groups, HOAs, community leaders, anti-tax groups
-   Incredible difficult to analyze systematically [@schneider1992]

## Motivations of boundary change entrepreneurs

-   Boundary change entrepreneurs have both a collective and selective goal
    -   The collective goal allows for the marshaling of support beyond the entrepreneur
    -   The selective goal is how the entrepreneur benefits from the change
-   Manufacturers seek economic development (collective) and individual or corporate financial gain (selective)

::: {.callout-important .large appearance="default" icon="false"}
## For this analysis,

The strength of manufacturers allows them to advocate for new districts and stave off the dissolution of older ones
:::

## Concern

-   Areas with declining numbers of special districts also have declining manufacturer strength
    -   This would give the appearance of a relationship with one does not necessarily exist
-   *Solution*: use exposure to Chinese import competition as a shock
    -   The endogeneity concern continues, special district might decline in areas with increased import exposure for unrelated reasons
    -   Instrument import exposure using Chinese imports to other developed countries [@autor2013]

## Import exposure

$$
\Delta IPW_{uit} = \sum_j \frac{L_{ijt}}{L_{ujt}}\frac{\Delta M_{ucjt}}{L_{it}}
$$

-   Import exposure is the decadal change in Chinese imports ($\Delta M_{ucjt}$) in industry *j* per worker ($L_{it}$), weighted by the local share ($L_{ijt}$) of national employment ($L_{ujt}$) in industry *j*
-   Higher levels of exposure indicates an increased likelihood of a weakened manufacturing base

## Instrument

$$
\Delta IPW_{oit} = \sum_j \frac{L_{ijt-1}}{L_{ujt-1}}\frac{\Delta M_{ocjt}}{L_{it-1}}
$$

-   The instrument is the decadal change in Chinese imports to other developed countries[^1] ($\Delta M_{ocjt}$) in industry *j* per worker in the previous decade ($L_{it-1}$), weighted by the local share ($L_{ijt-1}$) of national employment ($L_{ujt-1}$) in industry *j* in the previous decade

[^1]: Following @autor2013, eight high income countries: Australia, Denmark, Finland, Germany, Japan, New Zealand, Spain, and Switzerland.

## Analytical details

-   Period:
    -   RHS: 1991-2011, centering China's 2001 entry into the WTO
    -   LHS: 1992-2012, aligning with the Census of Governments
    -   Estimated as stacked, two-period 1991/1992-2011/2012 and pre/post ($n= 636$, balanced pre/post)
-   Unit of analysis:
    -   Commuting zone (1993), urban or urban adjacent[^2]
    -   Assumption that manufacturers, if acting like boundary change entrepreneurs, are most influential in the labor markets they contribute to

[^2]: Via rural-urban continuum codes (ERS) for the central city of the CZ--all metro codes (all central cities \> 250k) and central cities \> 20k and adjacent to a metro area.

##  {#slide-id data-menu-title="CZ Map"}

```{r coverage-map}
#| message: FALSE
#| warning: FALSE
#| results: asis
#| echo: false

library("sf")
library("urbnmapr")
library("directlabels")
library("ggtext")

## Import CZs
cz90 <- read_csv(file.path(datadir, "Census", "delineation-files", "czlma903.csv")) |>
  select(-c(cz80, distance)) |>
  mutate(
    fipstate = str_sub(state_place_code, 1, 2),
    county_fips = case_when(
      county_fips == "12025" ~ "12086",
      .default = county_fips
    ),
    cen_div = case_when(
      fipstate %in% c("09", "23", "25", "33", "44", "50") ~ "New England",
      fipstate %in% c("34", "36", "42") ~ "Middle Atlantic",
      fipstate %in% c("17", "18", "26", "39", "55") ~ "East North Central",
      fipstate %in% c("19", "20", "27", "29", "31", "38", "46") ~ "West North Central",
      fipstate %in% c("10", "11", "12", "13", "24", "37", "45", "51", "54") ~ "South Atlantic",
      fipstate %in% c("01", "21", "28", "47") ~ "East South Central",
      fipstate %in% c("05", "22", "40", "48") ~ "West South Central",
      fipstate %in% c("04", "08", "16", "30", "32", "35", "49", "56") ~ "Mountain",
      fipstate %in% c("02", "06", "15", "41", "53") ~ "Pacific",
    )
  )

# calculate "average" urban-rural score for each CZ
urban <- cz90 |>
  group_by(cz90) |>
  summarise(
    urban = min(as.numeric(urban_rural_code)),
    counties = n_distinct(county_fips)
  )


# Import underlying county data
counties_sf <- get_urbn_map("counties", sf = TRUE)
# Import underlying state data
census_sf <- get_urbn_map("states", sf = TRUE) |>
  filter(!state_abbv %in% c("AK", "HI")) |>
  mutate(
    cen_div = case_when(
      state_fips %in% c("09", "23", "25", "33", "44", "50") ~ "New England",
      state_fips %in% c("34", "36", "42") ~ "Middle Atlantic",
      state_fips %in% c("17", "18", "26", "39", "55") ~ "East North Central",
      state_fips %in% c("19", "20", "27", "29", "31", "38", "46") ~ "West North Central",
      state_fips %in% c("10", "11", "12", "13", "24", "37", "45", "51", "54") ~ "South Atlantic",
      state_fips %in% c("01", "21", "28", "47") ~ "East South Central",
      state_fips %in% c("05", "22", "40", "48") ~ "West South Central",
      state_fips %in% c("04", "08", "16", "30", "32", "35", "49", "56") ~ "Mountain",
      state_fips %in% c("02", "06", "15", "41", "53") ~ "Pacific",
    ),
    cen_region = case_when(
      cen_div %in% c("New England", "Middle Atlantic") ~ "Northeast",
      cen_div %in% c("East North Central", "West North Central") ~ "Midwest",
      cen_div %in% c("South Atlantic", "East South Central", "West South Central") ~ "South",
      cen_div %in% c("Mountain", "Pacific") ~ "West"
    )
  ) |>
  group_by(cen_region) |>
  summarise(across(geometry, ~ sf::st_union(.)), .groups = "drop")
state_sf <- get_urbn_map("states", sf = TRUE) |>
  filter(!state_abbv %in% c("AK", "HI"))

# Merge with CZ data and aggregate
analysis <- counties_sf |>
  left_join(cz90, by = c("county_fips" = "county_fips")) |>
  filter(state_abbv %ni% c("AK", "HI")) |>
  group_by(cz90) |>
  summarise(across(geometry, ~ sf::st_union(.)), .groups = "drop") |>
  left_join(urban, by = "cz90")

  ggplot() +
  #CZs
  geom_sf(data = filter(analysis, urban <= 4), mapping = aes(), fill = "grey", color = "#ffffff", linewidth = 0.5) +
  # States
  geom_sf(data = state_sf, mapping = aes(), fill = NA, color = "#333333", linewidth = 0.5) +
  # Regions
  geom_sf(data = census_sf, mapping = aes(), fill = NA, color = "#333333", linewidth = 1.25) +
  theme_minimal(base_family = "Public Sans") +
  theme(
    legend.position = "none",
    axis.line = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

```

## Model Specification

$$
\Delta G_{it} = \gamma_{t} + \beta_{1} \Delta IPW_{uit} + \mathbf{X}'\beta_2 + \epsilon_{it}
$$

-   where,
    -   $\Delta G_{it}$ is the decadal change in the net number of special districts in commuting zone *i*
    -   $\Delta IPW_{uit}$ is the change in import exposure, instrumented with $\Delta IPW_{oit}$
    -   $\gamma_{t}$ is included in the 1991-2011 regressions, excluded in the 1991-2001 or 2001-2011 regressions
    -   $X$ is a vector of control variables

## Baseline results

```{r results-setup}
#| message: FALSE
#| warning: FALSE
#| results: asis


# Main
all <- feols(
  nt_chg ~ pop1000|
    period |
    ipw ~ ipw_o,
  data = filter(analysis_vars, urban <= 4),
  vcov = cluster ~ cz90,
)

### Pre-WTO
pre_wto <- feols(
  nt_chg ~ pop1000 |
    ipw ~ ipw_o,
  data = filter(analysis_vars, urban <= 4) |>
    filter(period == "1991-2001"),
  vcov = cluster ~ cz90,
)

### Post-WTO
post_wto <- feols(
  nt_chg ~ pop1000  |
    ipw ~ ipw_o,
  data = filter(analysis_vars, urban <= 4) |>
    filter(period == "2001-2011"),
  vcov = cluster ~ cz90,
)

# Falsification 
all_f <- feols(
  nt_chg ~ pcy + pop1000 |
    period |
    ipw_c ~ ipw_o,
  data = filter(falsification_vars, urban <= 4),
  vcov = cluster ~ cz90,
)

### Pre-WTO
pre_wto_f <- feols(
  nt_chg ~ pcy + pop1000 |
    ipw_c ~ ipw_o,
  data = filter(falsification_vars, urban <= 4) |>
    filter(period == "1971-1981"),
  vcov = cluster ~ cz90,
)

### Post-WTO
post_wto_f <- feols(
  nt_chg ~ pcy + pop1000 |
    ipw_c ~ ipw_o,
  data = filter(falsification_vars, urban <= 4) |>
    filter(period == "1981-1991"),
  vcov = cluster ~ cz90,
)


models <-
  list(
    "1991-2001" = pre_wto, 
    "2001-2011" = post_wto, 
    "1991-2011" = all,
    "1971-1981" = pre_wto_f, 
    "1981-1991" = post_wto_f, 
    "1971-1991" = all_f
    )

cm <- c(
  "fit_ipw"     = "($\\Delta$ current period imports<br> from China to USA)/worker",
  "fit_ipw_c"   = "($\\Delta$ future period imports<br> from China to USA)/worker",
  "(Intercept)" = "Constant")

gm <- tibble::tribble(
  ~raw,        ~clean,          ~fmt,
  "nobs",      "N",             0)

modelsummary(
  models, 
  estimate = "{estimate}{stars}",
  stars = c("*" = .05, "**" = 0.01, "***" = .001),
  escape = FALSE,
  coef_omit = "Intercept|.*pop",
  coef_map = cm,
  gof_map = gm,
  gof_omit = "Std.Errors|FE: period|RMSE|DF|Deviance|R2|AIC|BIC"
  ) |>
  group_tt(j = list("I. 1991-2011" = 2:4, "II. 1971-1991 (pre-exposure)" = 5:7)) |>
  style_tt(i = -1, fontsize = 0.85) |>
  style_tt(i = 0:8, fontsize = 0.85)

```

## Baseline results

```{r results-display-2}
#| message: FALSE
#| warning: FALSE
#| results: asis
#| echo: false
# Main
all <- feols(
  nt_chg ~ pop1000|
    period |
    ipw ~ ipw_o,
  data = filter(analysis_vars, urban <= 4),
  vcov = cluster ~ cz90,
)

all_1 <- feols(
  nt_chg ~ pop1000 + total_dist|
    period |
    ipw ~ ipw_o,
  data = filter(analysis_vars, urban <= 4),
  vcov = cluster ~ cz90,
)

all_2 <- feols(
  nt_chg ~ pop1000 + total_dist|
    period + cen_region |
    ipw ~ ipw_o,
  data = filter(analysis_vars, urban <= 4),
  vcov = cluster ~ cz90,
)

all_3 <- feols(
  nt_chg ~ pop1000 + total_dist + pcy |
    period + cen_region |
    ipw ~ ipw_o,
  data = filter(analysis_vars, urban <= 4),
  vcov = cluster ~ cz90,
)

# Method here: https://lrberge.github.io/fixest/reference/coeftable.fixest.html
# Save out first stage coefficients
all_iv = coeftable(all, list = TRUE, stage = 1)
all_iv_1 = coeftable(all_1, list = TRUE, stage = 1)
all_iv_2 = coeftable(all_2, list = TRUE, stage = 1)
all_iv_3 = coeftable(all_3, list = TRUE, stage = 1)

## Method here: https://modelsummary.com/vignettes/modelsummary_extension.html#new-information-tidy_custom-and-glance_custom
# Save estimates from model 1 to dataframe
ti <- data.frame(
  term = "ipw_o",
  estimate = all_iv$ipw_o$coef,
  std.error = all_iv$ipw_o$se,
  p.value = all_iv$ipw_o$pvalue
)
# Register as a tidy object
mod <- list(
  tidy = ti)
class(mod) <- "modelsummary_list"
# Save estimates from model 2 to dataframe
ti_1 <- data.frame(
  term = "ipw_o",
  estimate = all_iv_1$ipw_o$coef,
  std.error = all_iv_1$ipw_o$se,
  p.value = all_iv_1$ipw_o$pvalue
)
# Register as a tidy object
mod_1 <- list(
  tidy = ti_1)
class(mod_1) <- "modelsummary_list"
# Save estimates from model 3 to dataframe
ti_2 <- data.frame(
  term = "ipw_o",
  estimate = all_iv_2$ipw_o$coef,
  std.error = all_iv_2$ipw_o$se,
  p.value = all_iv_2$ipw_o$pvalue
)
# Register as a tidy object
mod_2 <- list(
  tidy = ti_2)
class(mod_2) <- "modelsummary_list"
# Save estimates from model 4 to dataframe
ti_3 <- data.frame(
  term = "ipw_o",
  estimate = all_iv_3$ipw_o$coef,
  std.error = all_iv_3$ipw_o$se,
  p.value = all_iv_3$ipw_o$pvalue
)
# Register as a tidy object
mod_3 <- list(
  tidy = ti_3)
class(mod_3) <- "modelsummary_list"

# Stack models on top of each other
# Method: https://modelsummary.com/vignettes/modelsummary.html#string-rbind-or-rcollapse-panels-of-models-in-stacked-regression-tables
models <- list(
  "I. 1991-2011, stacked first differences" = list(
    "(1)" = all, 
    "(2)" = all_1, 
    "(3)" = all_2,
    "(4)" = all_3
    ),
  "II. 2SLS first stage estimates" = list(
    "(1)" = mod, 
    "(2)" = mod_1,
    "(3)" = mod_2, 
    "(4)" = mod_3
  ))

cm <- c(
  "fit_ipw"     = "($\\Delta$ imports from China to USA)/<br>worker",
  "pop1000"     = "Population",
  "total_dist"  = "Total districts",
  "pcy"         = "Income, per capita",
  "ipw_o"     = "($\\Delta$ imports from China to OTH)/<br>worker")

gm <- tibble::tribble(
  ~raw,        ~clean,          ~fmt,
  "nobs",      "N",             0)

rows <- tribble(
  ~term, ~"(1)", ~"(2)", ~"(3)", ~"(4)",
  "Census region dummies", "No", "No", "Yes", "Yes")

attr(rows, "position") <- 9

modelsummary(
  models, 
  stars = c("*" = .05, "**" = 0.01, "***" = .001),
  estimate = "{estimate}{stars}",
  shape = "rbind",
  escape = FALSE,
  coef_omit = "Intercept",
  coef_map = cm,
  #gof_map = gm,
  gof_omit = "Num.Obs.|Std.Errors|FE: cen_region|FE: period|RMSE|DF|Deviance|R2|AIC|BIC",
  add_rows = rows
  ) |>
  style_tt(i = -1, fontsize = 0.75) |>
  style_tt(i = 0:16, fontsize = 0.75)



```

## Newly created districts

```{r results-display-3}
#| message: FALSE
#| warning: FALSE
#| results: asis
#| echo: false

# Main
all <- feols(
  ne_tot ~ pop1000|
    period |
    ipw ~ ipw_o,
  data = filter(analysis_vars, urban <= 4),
  vcov = cluster ~ cz90,
)

all_1 <- feols(
  ne_tot ~ pop1000 + total_dist|
    period |
    ipw ~ ipw_o,
  data = filter(analysis_vars, urban <= 4),
  vcov = cluster ~ cz90,
)

all_2 <- feols(
  ne_tot ~ pop1000 + total_dist|
    period + cen_region |
    ipw ~ ipw_o,
  data = filter(analysis_vars, urban <= 4),
  vcov = cluster ~ cz90,
)

all_3 <- feols(
  ne_tot ~ pop1000 + total_dist + pcy |
    period + cen_region |
    ipw ~ ipw_o,
  data = filter(analysis_vars, urban <= 4),
  vcov = cluster ~ cz90,
)


models <-
  list(
    "(1)" = all, 
    "(2)" = all_1, 
    "(3)" = all_2,
    "(4)" = all_3
    )

cm <- c(
  "fit_ipw"     = "($\\Delta$ imports from China to USA)/<br>worker",
  "pop1000"     = "Population",
  "total_dist"  = "Total districts",
  "pcy"         = "Income, per capita")

gm <- tibble::tribble(
  ~raw,        ~clean,          ~fmt,
  "nobs",      "N",             0)

rows <- tribble(
  ~term, ~"(1)", ~"(2)", ~"(3)", ~"(4)",
  "Census region dummies", "No", "No", "Yes", "Yes")

attr(rows, "position") <- 9

modelsummary(
  models, 
  estimate = "{estimate}{stars}",
  stars = c("*" = .05, "**" = 0.01, "***" = .001),
  escape = FALSE,
  coef_omit = "Intercept",
  coef_map = cm,
  gof_map = gm,
  gof_omit = "Std.Errors|FE: cen_region|FE: period|RMSE|DF|Deviance|R2|AIC|BIC",
  add_rows = rows
  ) |>
  group_tt(j = list("1991-2011, stacked first differences" = 2:5)) #|>
  #style_tt(i = -1, fontsize = 0.85) |>
  #style_tt(i = 0:9, fontsize = 0.85)


```

## Dissolved districts

```{r results-display-4}
#| message: FALSE
#| warning: FALSE
#| results: asis
#| echo: false

# Main
all <- feols(
  nx_tot ~ pop1000|
    period |
    ipw ~ ipw_o,
  data = filter(analysis_vars, urban <= 4),
  vcov = cluster ~ cz90,
)

all_1 <- feols(
  nx_tot ~ pop1000 + total_dist|
    period |
    ipw ~ ipw_o,
  data = filter(analysis_vars, urban <= 4),
  vcov = cluster ~ cz90,
)

all_2 <- feols(
  nx_tot ~ pop1000 + total_dist|
    period + cen_region |
    ipw ~ ipw_o,
  data = filter(analysis_vars, urban <= 4),
  vcov = cluster ~ cz90,
)

all_3 <- feols(
  nx_tot ~ pop1000 + total_dist + pcy |
    period + cen_region |
    ipw ~ ipw_o,
  data = filter(analysis_vars, urban <= 4),
  vcov = cluster ~ cz90,
)


models <-
  list(
    "(1)" = all, 
    "(2)" = all_1, 
    "(3)" = all_2,
    "(4)" = all_3
    )

cm <- c(
  "fit_ipw"     = "($\\Delta$ imports from China to USA)/<br>worker",
  "pop1000"     = "Population",
  "total_dist"  = "Total districts",
  "pcy"         = "Income, per capita")

gm <- tibble::tribble(
  ~raw,        ~clean,          ~fmt,
  "nobs",      "N",             0)

rows <- tribble(
  ~term, ~"(1)", ~"(2)", ~"(3)", ~"(4)",
  "Census region dummies", "No", "No", "Yes", "Yes")

attr(rows, "position") <- 9

modelsummary(
  models, 
  estimate = "{estimate}{stars}",
  stars = c("*" = .05, "**" = 0.01, "***" = .001),
  escape = FALSE,
  coef_omit = "Intercept",
  coef_map = cm,
  gof_map = gm,
  gof_omit = "Std.Errors|FE: cen_region|FE: period|RMSE|DF|Deviance|R2|AIC|BIC",
  add_rows = rows
  ) |>
  group_tt(j = list("1991-2011, stacked first differences" = 2:5)) #|>
  #style_tt(i = -1, fontsize = 0.85) |>
  #style_tt(i = 0:9, fontsize = 0.85)


```

## Conclusions

-   Depending on the specification, a \$1,000 increase in import exposure per worker leads to between 1.9 and 3.1 district reduction among urban and urban adjacent commuting zones
    -   The results appear driven by a reduction in newly created districts
-   As manufacturers
    -   decline in local influence or
    -   their relative demand for services declines
-   The necessity for new districts also declines and fewer districts are created

## Conclusions {visibility="hidden"}

-   As @schneider1992 note, identifying political entrepreneurs (of which, boundary change entrepreneurs are a subset) is exceedingly difficult outside of rigorous case studies

-   While not perfect, looking for shocks to groups that may contain such entrepreneurs can attempt to approximate their impact

-   This study demonstrates that approach is viable

# Thank you {.slide-bg-red visibility="uncounted"}

## References {visibility="uncounted"}

::: {#refs}
:::